Stochastic blockmodeling of relational event dynamics

### 2012-06-01 docs/discussion.tex
Update results tables to save some space.

%This analysis suggests 
Our approach has the ability to uncover systematic differences in dynamic behaviors among subsets of nodes, even in the absence of differences in marginal interaction rates.
% across a variety of data sets.
The analyses of Section \ref{sec:experiments} show that this model family has improved predictive accuracy over baseline methods on real data with respect to ranking tasks and the likelihood of unobserved data.
In particular, our proposed approach leads to improved predictive accuracy when compared to both (a) relational event models that lack latent clusters, and (b) stochastic blockmodels for count data, both of which are special cases of our model family.
Though prediction is not the main focus of our effort, these results provide evidence that having latent structure (i.e. K>1) can lead to improvements in predictive power. However, our prediction results also show that it is easy to overfit with this model family. 
%If we restrict to K=2 on these small data sets, we systematically outperform the K=1 model. 
%{\red (TODO: confirm this)}
 As K increases beyond 2 (e.g., for the unrestrained CRP prior), these models are prone to overfit. This is not surprising, given that the number of fitted parameters scales as the square of the number of components K in the model. A natural direction worth exploring for this family is a class of priors that are more resistant to overfitting (e.g., by imposing more structure on the parameters within each group).

>>>>

%This analysis suggests 
Our approach has the ability to uncover systematic differences in dynamic behaviors among subsets of nodes, even in the absence of differences in marginal interaction rates.
% across a variety of data sets.
The analyses of Section \ref{sec:experiments} show that this model family has improved predictive accuracy over baseline methods on real data with respect to ranking tasks and the likelihood of unobserved data.
In particular, our proposed approach leads to improved predictive accuracy when compared to both (a) relational event models that lack latent clusters, and (b) stochastic blockmodels for count data, both of which are special cases of our model family.
Though prediction is not the main focus of our effort, these results provide evidence that having latent structure (i.e. $K > 1$) can lead to improvements in predictive power. However, our prediction results also show that it is easy to overfit with this model family. 
%If we restrict to K=2 on these small data sets, we systematically outperform the K=1 model. 
%{\red (TODO: confirm this)}
 As $K$ increases beyond 2 (e.g., for the unrestrained CRP prior), these models are prone to overfit. This is not surprising, given that the number of fitted parameters scales as the square of the number of components $K$ in the model. A natural direction worth exploring for this family is a class of priors that are more resistant to overfitting (e.g., by imposing more structure on the parameters within each group).

### 2012-06-01 docs/experiments.tex
Update results tables to save some space.

In addition, we compute recall to evaluate whether the next observed event is among the most likely according to the model.
At each event $m$ we sort the predicted intensities of all possible events in decreasing order, find the rank of the observed event in the list of predicted intensities, and compute the mean rank across the $M$ events.

{ \scriptsize
\input{../figs/results-llk4.tex}
\input{../figs/results-recall-all.tex}
}
%\subsection{Baselines}

>>>>

In addition, we compute recall to evaluate whether the next observed event is among the most likely according to the model.
At each event $m$ we sort the predicted intensities of all possible events in decreasing order, find the rank of the observed event in the list of predicted intensities, and compute the mean number of events ranking above cutoffs $\kappa=5$ and $\kappa=20$.

\input{../figs/results-llk4.tex}
\input{../figs/results-recall-all.tex}
